Fusion Moves for Correlation Clustering

### 2014-11-10 paper/egpaper_for_review.tex
fixed errors in 2 plots

\subsection{Define Fusion on Segmentations}

Given two proposal solutions $y'$ and $y''$
the fusion move between those solutions is defined
as follows:

Let the $\bar{y}$ be the edge wise or of  $y'$ and $y''$.
\begin{equation}
\breve{y} =  y' \cup y''.
\end{equation}
Contraction of all edges in $G$ where $\bar{y}=0$ defines
a smaller graph $G_{\bar{y}}$ and the corresponding
edge weights $W_{\hat{y}}$.
Any cut $\bar{y}$ on $G_{\hat{y}}$ induces a cut $y$ on $G$.
The function 
$\rho_y^{-1}$ maps a cut from $G_{\hat{y}}$  to $G$

\begin{equation}
   \rho_y^{-1} : P(G_y) \to P(G)
\end{equation}

Therefore solving eq. \ref{eq:edgeproblem} 
on $G_{\hat{y}}$
leads to a cut on $G$ which is guaranteed to 
to have a better or equal energy
then any of the two proposal solutions.

@@

\begin{center}
    \begin{eqnarray}
        y 
        &=& 
        \rho_{\hat{y}}^{-1}(
        \argmin_{y \in MC(G_{\hat{y}})\cap \{0,1\}^{|E_{\hat{y}}|}} 
        \sum_{ (i,j) \in E_{\hat{y}} } 
        w^{\hat{y}}_{ij} \cdot \bar{y}_{ij} 
    \end{eqnarray}
\end{center}

\begin{center}
    \begin{eqnarray}
      y \cdot w \leq \min(y'\cdot w,  y'' \cdot w) 
    \end{eqnarray}
\end{center}

>>>>

@@

% \begin{center}
%     \begin{eqnarray}
%         y 
%         &=& 
%         \rho_{\hat{y}}^{-1}(
%         \argmin_{y \in MC(G_{\hat{y}})\cap \{0,1\}^{|E_{\hat{y}}|}} 
%         \sum_{ (i,j) \in E_{\hat{y}} } 
%         w^{\hat{y}}_{ij} \cdot \bar{y}_{ij} 
%     \end{eqnarray}
% \end{center}

% \begin{center}
%     \begin{eqnarray}
%       y \cdot w \leq \min(y'\cdot w,  y'' \cdot w) 
%     \end{eqnarray}
% \end{center}

### 2014-11-10 paper/inputs/fig_hc_alg.tex
update related work, relayout Figure EHC
fixed errors in 2 plots

\tikzstyle{nS}=[circle,minimum size = 0.3cm,inner sep = 0pt,draw, font=\small,align=left]
\tikzstyle{eS}=[thick,minimum size = 0.5cm,inner sep = 0pt,draw, font=\small,align=left]
\tikzstyle{eC}=[very thick,minimum size = 0.5cm,inner sep = 0pt,draw=red, font=\small,align=left]
\tikzstyle{eNC}=[very thick,minimum size = 0.5cm,inner sep = 0pt,draw=green, font=\small,align=left]
\tikzstyle{eNS}=[fill=white,minimum size = 0.5cm,inner sep = 0pt, font=\tiny,align=left]

\begin{center}
\begin{figure}
\resizebox{!}{0.30\linewidth}{%
    \begin{tikzpicture}
    \draw (0,-1)node (dummyLow){} ;
    \draw (0, 3)node (dummyLow){} ;
    \draw (2,2) node[nS] (n0) {$0$}; 
    \draw (4,2) node[nS] (n1) {$1$};
    \draw (6,2) node[nS] (n2) {$2$};
    \draw (2,0) node[nS] (n3) {$3$}; 
    \draw (4,0) node[nS] (n4) {$4$};
    \draw (6,0) node[nS] (n5) {$5$};

@@

    \path
        (n03) edge[eS] node[eNS]{$w_{01}=-1$} (n1) 
        (n1) edge[eS] node[eNS]{$w_{12}=-2$} (n2) 
        (n03) edge[eS] node[eNS]{$w_{34}-2$} (n4) 
        (n4) edge[eS] node[eNS]{$w_{45}=1$} (n5)
        (n1) edge[eS] node[eNS]{$w_{14}=1$} (n4)
        (n2) edge[eC] node[eNS]{$w_{25}=3$} (n5)
    ;
    \end{tikzpicture}
}

\resizebox{!}{0.30\linewidth}{%
    \begin{tikzpicture}
    \draw (0,-1)node (dummyLow){} ;
    \draw (0, 3)node (dummyLow){} ;
    \draw (2,1) node[nS] (n03) {$\{0,3\}$}; 
    \draw (4,2) node[nS] (n1) {$1$};
    \draw (6,1) node[nS] (n25) {$\{2,5\}$};
    \draw (4,0) node[nS] (n4) {$4$};
    \path
        (n03) edge[eS] node[eNS]{$w_{01}=-1$} (n1) 
        (n1) edge[eS] node[eNS]{$w_{12}=-2$} (n25) 
        (n03) edge[eS] node[eNS]{$w_{34}=-2$} (n4) 
        (n4) edge[eS] node[eNS]{$w_{45}=1$} (n25)
        (n1) edge[eC] node[eNS]{$w_{14}=2$} (n4)
    ;
    \end{tikzpicture}
    \begin{tikzpicture}
    \draw (0,-1)node (dummyLow){} ;
    \draw (0, 3)node (dummyLow){} ;
    \draw (2,1) node[nS] (n03) {$\{0,3\}$}; 
    \draw (4,1) node[nS] (n14) {$\{1,4\}$};
    \draw (6,1) node[nS] (n25) {$\{2,5\}$};
    \path
        %(n03) edge[eS] node[eNS]{$w_{01}$} (n1) 
        (n14) edge[eNC] node[eNS]{$w_{12}+$\\$w_{45}=$\\$-1$} (n25) 
        (n03) edge[eS] node[eNS]{$w_{01}+$\\$w_{34}=$\\$-3$} (n14) 
    ;
    \end{tikzpicture}
}
\caption{
    To use hierarchical clustering as an approximator for
    the multicut objective we contract the edge with the highest weight
    in each step (to be contracted edge is shown in red). 
    Whenever multiple edges are merged into a single edge,
    we use the sum of the weight as a new weight, since
    we have to pay for all edges which are cut in the uncontracted 
    graph.
    We stop when the highest edge weight is smaller
    or equal to zero (edge shown in green).
}\label{fig:hc_alg}
\end{figure}
\end{center}

>>>>

\tikzstyle{nS}=[circle,minimum size = 0.6cm,inner sep = 0pt,draw, font=\small,align=left]
\tikzstyle{eS}=[thick,minimum size = 0.5cm,inner sep = 0pt,draw, font=\small,align=left]
\tikzstyle{eC}=[very thick,minimum size = 0.5cm,inner sep = 0pt,draw=red, font=\small,align=left]
\tikzstyle{eNC}=[very thick,minimum size = 0.5cm,inner sep = 0pt,draw=green, font=\small,align=left]
\tikzstyle{eNS}=[fill=white,minimum size = 0.5cm,inner sep = 0pt, font=\tiny,align=left]

\begin{center}
\begin{figure*}
\resizebox{!}{0.15\linewidth}{%
    \begin{tikzpicture}
    \draw (0,-1)node (dummyLow){} ;
    \draw (0, 3)node (dummyLow){} ;
    \draw (2,2) node[nS] (n0) {$0$}; 
    \draw (4,2) node[nS] (n1) {$1$};
    \draw (6,2) node[nS] (n2) {$2$};
    \draw (2,0) node[nS] (n3) {$3$}; 
    \draw (4,0) node[nS] (n4) {$4$};
    \draw (6,0) node[nS] (n5) {$5$};

@@

    \path
        (n03) edge[eS] node[eNS]{$w_{01}=-1$} (n1) 
        (n1) edge[eS] node[eNS]{$w_{12}=-2$} (n2) 
        (n03) edge[eS] node[eNS]{$w_{34}-2$} (n4) 
        (n4) edge[eS] node[eNS]{$w_{45}=1$} (n5)
        (n1) edge[eS] node[eNS]{$w_{14}=2$} (n4)
        (n2) edge[eC] node[eNS]{$w_{25}=3$} (n5)
    ;
    \end{tikzpicture}
}
%
\resizebox{!}{0.15\linewidth}{%
    \begin{tikzpicture}
    \draw (0,-1)node (dummyLow){} ;
    \draw (0, 3)node (dummyLow){} ;
    \draw (2,1) node[nS] (n03) {$\{0,3\}$}; 
    \draw (4,2) node[nS] (n1) {$1$};
    \draw (6,1) node[nS] (n25) {$\{2,5\}$};
    \draw (4,0) node[nS] (n4) {$4$};
    \path
        (n03) edge[eS] node[eNS]{$w_{01}=-1$} (n1) 
        (n1) edge[eS] node[eNS]{$w_{12}=-2$} (n25) 
        (n03) edge[eS] node[eNS]{$w_{34}=-2$} (n4) 
        (n4) edge[eS] node[eNS]{$w_{45}=1$} (n25)
        (n1) edge[eC] node[eNS]{$w_{14}=2$} (n4)
    ;
    \end{tikzpicture}
    \begin{tikzpicture}
    \draw (0,-1)node (dummyLow){} ;
    \draw (0, 3)node (dummyLow){} ;
    \draw (2,1) node[nS] (n03) {$\{0,3\}$}; 
    \draw (4,1) node[nS] (n14) {$\{1,4\}$};
    \draw (6,1) node[nS] (n25) {$\{2,5\}$};
    \path
        %(n03) edge[eS] node[eNS]{$w_{01}$} (n1) 
        (n14) edge[eNC] node[eNS]{$w_{12}+$\\$w_{45}=$\\$-1$} (n25) 
        (n03) edge[eS] node[eNS]{$w_{01}+$\\$w_{34}=$\\$-3$} (n14) 
    ;
    \end{tikzpicture}
}
\caption{
    To use hierarchical clustering as an approximator for
    the multicut objective we contract the edge with the highest weight
    in each step (to be contracted edge is shown in red). 
    Whenever multiple edges are merged into a single edge,
    we use the sum of the weight as a new weight, since
    we have to pay for all edges which are cut in the uncontracted 
    graph.
    We stop when the highest edge weight is smaller
    or equal to zero (edge shown in green).
}\label{fig:hc_alg}
\end{figure*}
\end{center}
